Case-based Arabic Morphological Analysis

### 2010-12-12 trunk/tex/sarf.tex
added the progress report for LNCSR

%
% File naaclhlt2010.tex
%
% Contact: nasmith@cs.cmu.edu

@@

\usepackage{utf8}
\setarab
\fullvocalize
%\transtrue
\arabtrue

\newcommand{\CharCodeIn}[1]{`\CodeIn{#1}'}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}

@@

%\title{Instructions for NAACL HLT 2010 Proceedings\Thanks{This...}}
\title{Case based Arabic Morphological Analysis with 
    Compositional Non-deterministic Automata }

%\author{ Jad Makhlouta \\
%  \And
%Hamza Harkous \\
%  American University of Beirut \\
%  {\tt \{jem04, hhh20, fz11\}@aub.edu.lb }
%  \And 
%  Fadi Zaraket 
%}

@@

We validate our hypothesis using a case study from the Islamic 
literature. 
A {\em hadith} is a narration related to the prophet Mohammad
through a {\em sanad} or a sequence of narrators. 
The authentication of a hadith highly depends on the credibility
of each of the narrators as reported in separate biography 
books. 
In this paper we consider the problem of automatically segmenting
a hadith book into narrations, then segmenting each narration into
its content or {\em matn} and its sanad.
We also partition the sanad accurately into the 
separate narrators so that we can later look each one of them 
up in the biography books.

@@

\begin{figure*}[tb]
\center{
\resizebox{1.7\columnwidth}{!}
{ \input{psfigs/FSM.pstex_t}}
\caption{Example composition of the prefix, stem and suffix FSAs.}
\label{f:example}
}
\end{figure*}
% the FSMs for the three words

The compositional FSA diagram in Figure~\ref{f:example}
illustrates the operation of Sarf when parsing the
string \RL{al-lA`bwn}\RL{wsyl`b-h-aa}.
\footnote{ 
\RL{n}%
\RL{w}
\RL{b}
\RL{`}
\RL{a} 
\RL{l}
\RL{l}
\RL{a} %
\RL{a}
\RL{h}
\RL{b}
\RL{`}
\RL{l}
\RL{y}
\RL{s}
\RL{w}
in separate form to ease following the example
}
The square and circle legends are states of the FSA
and the directed edges are transitions driven by an input
letter that matches the label of the edge. 
The square denotes an accept state, 
the circle denotes a regular state, and the reject states
are omitted for clarity. 
Figure~\ref{f:example}(a) represents the prefix FSA and 
Figures~\ref{f:example}(b) and~\ref{f:example}(c) represent the 
stem and suffix FSAs respectively. 
The symbol $\epsilon$ represents an empty string and is 
the source of non-determinism in this example.

We start at the root square state in the prefix FSA
which is an accept state. 
The edge labeled $\epsilon$ connects the prefix 
FSA to the stem FSA and transitions from any accept state
in the prefix FSA to the root state in the stem FSA.
The edge that connects the stem FSA to the suffix FSA
follows the same behavior.

When there are two valid transitions such as \RL{w} 
and $\epsilon$ in the start case, the non-deterministic 
FSA $\Phi$ spawns an exact copy of itself $\Psi$. FSA $\Phi$
makes one transition, and FSA $\Psi$ makes the other. 
Each of the FSAs now represent a valid analysis so far. 
When the FSA is at a state where the next input letter
leads to a reject state, the FSA dies.
The reject states are omitted from Figure~\ref{f:example}
and are denoted by the absence of the corresponding 
letters. 
In our example, if we assume there were no stems that start 
with the letter \RL{w}, $\Psi$ will die then. 
In reality probably $\Psi$ will die when the input string
is at \RL{wsyl`}.

Note that the prefix and affix FSAs allow recursive 
prefixes. For example, \RL{w} will result in an accept state
that transitions to the stem FSA. 
When \RL{s} follows, we move to another accept state in the 
prefix FSA corresponding to the suffix \RL{ws}. 
The same applies to the suffix FSA.

Lets consider FSA $\Phi$ after it consumed \RL{wsy} 
and transitioned into the stem FSA root node. 
Now $\Phi$ will transition with \RL{l`b} to reach an accept 
state. 
Before moving with the letter \RL{b} to the accept state,
$\Phi$ needs to make sure that the stem \RL{l`b} is compatible
with the prefix \RL{wsy}. 
It does that by associating a category value for each accept state. 
Sarf considers the value of the category as part of the state.
Thus each state shown in Figure~\ref{f:example} actually represents
more than one state. 
If the category of \RL{l`b} is compatible with the category of
\RL{wsy} then \RL{b} will move $\Phi$ to an accept state. 
Otherwise, it will move it to a regular or a reject state.

Since $\Phi$ is now in an accept state in the stem FSA, it will
spawn $\Sigma$ that transitions into the root of the 
suffix FSA. When \RL{h} is consumed, $\Phi$ will die since 
there is no edge from the current state labeled with \RL{h}. 
Now $\Sigma$ represents a valid analysis and can proceed.

Note that $\Sigma$ reports a full word at any accept state
by spawning a new Automata using the $\epsilon$ transition
to the prefix FSA.
In Sarf, this only happens with white space, delimiters, 
and non-connecting letters. 
We left that out in Figure~\ref{f:example} for clarity.

Finally, the case-based controller can interfere at any point in the 
analysis to make a decision like ignoring an Automata that 
is not interesting. 
It may also decide to correct the analysis of one Automata
based on the decision of the others.

@@

A hadith in Islamic literature is a narration from the prophet Mohammad
related by multiple narrators.
Establishing the authenticity of a hadith is an important task
in Islamic studies. 
%Several researchers~\cite{Hadithopaedia:08} attempted to automate 
%the analysis of the hadith literature. 
In this paper we use Sarf to successfully automate the
analysis of three books of hadith selected 
arbitrarily~\cite{IbnHanbal,AlKulayni,AlTousi}\footnote{We obtained
  the digitized books from online sources such as 
  \href{http://www.yasoob.com/}{http://www.yasoob.com/} and 
  \href{http://www.al-eman.com/}{http://www.al-eman.com/}. }
%  Our understanding is that those books are historical documents with 
 % public IP.}.

@@

\subsection{Controller}
% FSM for the controller

We illustrate the hadith case-based controller FSA 
in Figure~\ref{f:hadith}. 
The transitions in the hadith FSA are excited
by inputs from the Sarf morphological analyzer. 
A NAME label means that Sarf encountered a proper name.
An NRC label means that Sarf met a narrator connector such as
\RL{`an} "on behalf of", \RL{.hada_t} "narrated", \RL{qaal} "said", 
\RL{'a_hbar} "told" or one of their derivations. 
The IBN label corresponds to the word \RL{ibn} "the son of" and is a name connector.
The NISBA label corresponds to the an adjective that points to a person such 
as \RL{alma.sriy} "the Egyptian".

@@

The controller has four states that correspond to 
an abstract position in text relative to the next sanad. 
State TEXT\_S is the initial state and denotes that
the controller is outside the context of a sanad.
The controller moves to the state NAME\_S whenever
NAME is reported by Sarf.
State NRC\_S means that the controller thinks it is in the context
of a narrator name after Sarf reports an NRC.
Similarly, state NMC\_S
indicates that the controller expects a name to appear within 
a tolerance threshold expressed by 
$\tau_{\mbox{NMC}}$ and $\lambda_{\mbox{NMC}}$.

\begin{figure}[tb!]
\center{
\resizebox{.9\columnwidth}{!}
{ \input{psfigs/hadith.pstex_t}}
\caption{FSA controller of the hadith case study.}
\label{f:hadith}
}
\end{figure}

@@

The FSA reports a valid chain of narrators when a sequence of names
connected by narrator connectors appears. 
It marks the beginning of the hadith with the beginning of the current sequence,
and marks the end of the hadith with the beginning of the next sequence. 
It also marks the chain of narrators as the sequence itself.

The definition of input labels such as NAME and IBN depends on the 
morphological analyzer. 
However, our case-based controller approach was able to perform well
under both a good analyzer and a refined one.

@@

\begin{table*}[bt]
\centering
\caption{Results of the hadith case study with Sarf.}
%\begin{tabular}{|p{1.5cm}||c|c||c|c||c|c|} \hline
\begin{tabular}{lp{.2cm}ccp{.2cm}ccp{.2cm}cc} %\cline{2-10}
 & & \multicolumn{2}{c}{Al Kafi} & & \multicolumn{2}{c}{Al Istibsar} & &\multicolumn{2}{c}{Ibn Hanbal} \\ \cline{3-10}
 & & Simple & Refined & & Simple & Refined & & Simple  & Refined \\\bottomrule  %\hline \hline
Word count & &\multicolumn{2}{c}{98,943} & & \multicolumn{2}{c}{103,835} & & \multicolumn{2}{c}{20,354} \\ 
 Names      & & 20,473 & 12,060  & &20,646 &  14,613& & 4,762 & 3,013\\
Names/Narrator& &2.48 & 1.97 & & 2.17 &  1.84& & 1.49 & 1.25 \\
Narrators & &3,080 & 2,623 & & 6,164 &  5,767& & 2,082 & 1,755 \\ 
Narrators/Chain & & 5.28 & 4.84 & & 4.98&  4.76 & & 4.8 &4.05 \\
Chains & & 583 & 542 &  & 1,238& 1,211& & 433 & 433 \\ 
Ignored names & & 11,801 & 6,400 &  & 5,845 & 3,348 & & 1,386 & 642 \\ \hline
Segmentation accuracy & & 85\% & 96\%& & 96\%& 96\%& & 92\%& 92\%\\ 
Chain accuracy & & 99\% & 99\%&  & 98\%& 99\%& & 99\% & 97\% \\ 
%Narrator accuracy & & & & & &  & & & \\ 
Narrator name accuracy & & 93\% & 91\%& &  92\%& 90\% & & 90\% & 90\% \\ \hline
Name false positives & & 28\% & 7\%&  & 9\%& 4\% & & 34\% & 4\% \\ \hline
Sarf running time (secs.)& & 24.5 & 22.67 & & 23.5 & 23.17 & & 2.25 & 1.67\\ \hline
\end{tabular}
\normalsize
\label{t:hadithresallresults}
\end{table*}

To evaluate our hypothesis of the utility of a case-based morphological analyzer,
we ran our case study in two modes, simple and refined.
In the simple mode, Sarf is controlled by the hadith controller.
In the refined mode, we apply several refinements to Sarf.
The first refinement removes female proper names since they do not occur often in
hadith.
We also add a refinement that detects compound names as they are common in narrator
names.
Finally, we consider a possessive form as a reference to a person and treat
it as a narrator.

@@

\section{Future Work}
\label{sec:future}

@@

>>>>

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu

@@

\usepackage{utf8}
\setarab
\fullvocalize
\transtrue
\arabtrue

\newcommand{\CharCodeIn}[1]{`\CodeIn{#1}'}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
\newcommand{\frl}[1]{\fbox{\RL{#1}}} 
\newcommand{\noArRL}[1]{\arabfalse\RL{#1}\arabtrue} 
\newcommand{\noTrRL}[1]{\transfalse\RL{#1}\transtrue}

@@

%\title{Instructions for NAACL HLT 2010 Proceedings\Thanks{This...}}
\title{Case-based Arabic Morphological Analysis }

\author{ Jad Makhlouta \\
  \And
Hamza Harkous \\
  American University of Beirut \\
  {\tt \{jem04, hhh20, fz11\}@aub.edu.lb }
  \And 
  Fadi Zaraket 
}

@@

\transfalse
\begin{figure}[tb]
\center{
\resizebox{1.2\columnwidth}{!}
{ \input{psfigs/exhadith.pstex_t}}
\caption{Hadith abstraction example.}
\label{f:exhadith}
}
\end{figure}
% the FSMs for the three words
\transtrue

We validate our hypothesis using a case study from the Islamic 
literature. 
A \RL{.hady_t} is a narration related to the prophet Mohammad
through a \RL{sanad} or a sequence of narrators. 
Figure~\ref{f:exhadith} shows an example \noArRL{.hady_t} in Arabic with its 
transliteration and translation. 
The authentication of a \noArRL{.hady_t} highly depends on the credibility
of each of the narrators as reported in separate biography 
books. 
In this paper we consider the problem of automatically segmenting
a \noArRL{.hady_t} book into narrations, then segmenting each narration into
its content or \RL{matn} and its \noArRL{sanad}.
We also partition the sanad accurately into the 
separate narrators so that we can later look each one of them 
up in the biography books. 
For example, the boxes in Figure~\ref{f:exhadith} are proper names and once
connected toghether they form complex names of narrators. For example
narrator $n_1$ has the first name \noTrRL{qtybT} and his father name is
\noTrRL{s`yd} as the word in between \noTrRL{bn} (son of) indicates.

@@

\transfalse
\begin{figure*}[tb]
\center{
\resizebox{1.7\columnwidth}{!}
{ \input{psfigs/FSM.pstex_t}}
\caption{Example composition of the prefix, stem and suffix transducers.}
\label{f:example}
}
\end{figure*}
% the FSMs for the three words
\transtrue

The diagram in Figure~\ref{f:example}
illustrates the operation of Sarf when parsing the
string \RL{al-lA`bwn}\RL{wsyl`b-h-aa}.
\footnote{ 
\RL{n}%
\RL{w}
\RL{b}
\RL{`}
\RL{a} 
\RL{l}
\RL{l}
\RL{a} %
\RL{a}
\RL{h}
\RL{b}
\RL{`}
\RL{l}
\RL{y}
\RL{s}
\RL{w}
in separate form to ease following the example
}
The square and circle legends are states 
and the directed edges are transitions driven by an input
letter that matches the label of the edge. 
The square denotes an accept state, 
the circle denotes a regular state, and the reject states
are omitted for clarity. 
Figure~\ref{f:example}(a) represents the prefix transducer and 
Figures~\ref{f:example}(b) and~\ref{f:example}(c) represent the 
stem and suffix transducers respectively. 
The symbol $\epsilon$ represents an empty string and is 
the source of non-determinism in this example.

We start at the root square state in the prefix transducer
which is an accept state. 
The edge labeled $\epsilon$ connects the prefix 
transducer to the stem transducer and transitions from any accept state
in the prefix transducer to the root state in the stem transducer.
The edge that connects the stem transducer to the suffix transducer
follows the same behavior.

When there are two valid transitions such as \RL{w} 
and $\epsilon$ in the start case, the non-deterministic 
composition $\Phi$ spawns an exact copy of itself $\Psi$. 
$\Phi$ makes one transition, and $\Psi$ makes the other. 
Each of $\Phi$ and $\Psi$ now represent a valid analysis so far. 
When $\Phi$ or $\Psi$ is at a state where the next input letter
leads to a reject state, it dies.
The reject states are omitted from Figure~\ref{f:example}
and are denoted by the absence of the corresponding 
letters. 
In our example, if we assume there were no stems that start 
with the letter \RL{w}, $\Psi$ will die then. 
In reality probably $\Psi$ will die when the input string
is at \RL{wsyl`}.

Note that the prefix and affix transducers allow recursive 
prefixes. For example, \RL{w} will result in an accept state
that transitions to the stem transducer. 
When \RL{s} follows, we move to another accept state in the 
prefix transducer corresponding to the suffix \RL{ws}. 
The same applies to the suffix transducer.

Lets consider $\Phi$ after it consumed \RL{wsy} 
and transitioned into the stem transducer root node. 
Now $\Phi$ will transition with \RL{l`b} to reach an accept 
state. 
Before moving with the letter \RL{b} to the accept state,
$\Phi$ needs to make sure that the stem \RL{l`b} is compatible
with the prefix \RL{wsy}. 
It does that by associating a category value for each accept state. 
Sarf considers the value of the category as part of the state.
Thus each state shown in Figure~\ref{f:example} actually represents
more than one state. 
If the category of \RL{l`b} is compatible with the category of
\RL{wsy} then \RL{b} will move $\Phi$ to an accept state. 
Otherwise, it will move it to a regular or a reject state.

Since $\Phi$ is now in an accept state in the stem transducer, it will
spawn $\Sigma$ that transitions into the root of the 
suffix transducer. When \RL{h} is consumed, $\Phi$ will die since 
there is no edge from the current state labeled with \RL{h}. 
Now $\Sigma$ represents a valid analysis and can proceed.

Note that $\Sigma$ reports a full word at any accept state
by spawning a new composition using the $\epsilon$ transition
to the prefix transducer.
In Sarf, this only happens with white space, delimiters, 
and non-connecting letters. 
We left that out in Figure~\ref{f:example} for clarity.

Finally, the case-based controller can interfere at any point in the 
analysis to make a decision like ignoring a composition that 
is not interesting. 
It may also decide to correct the analysis of one Automata
based on the decision of the others. 
The controller uses the output of the transducers as input
to make its decision. 
It does not produce any output and therefore the composition
of the three transducers with the controller is a finite 
state Automaton (FSA).

@@

A hadith in Islamic literature is a narration from the prophet Mohammad
related by multiple narrators.
Establishing the authenticity of a hadith is an important task
in Islamic studies. 
Based on that Islamic scholars issue rules that affect the life
of people around the world. 
The literature lacks an exhaustive mechanism of authentication
check as. This is currently manual work prone to error and almost
impossible to complete in the life time of a scholar due to the
large literature available. 
%Several researchers~\cite{Hadithopaedia:08} attempted to automate 
%the analysis of the hadith literature. 
In this paper we use Sarf to successfully automate the
analysis of three books of hadith selected 
arbitrarily~\cite{IbnHanbal,AlKulayni,AlTousi}\footnote{We obtained
  the digitized books from online sources such as 
  \href{http://www.yasoob.com/}{http://www.yasoob.com/} and 
  \href{http://www.al-eman.com/}{http://www.al-eman.com/}. }
%  Our understanding is that those books are historical documents with 
 % public IP.}.

%\setcode{utf8}
%\begin{arabtext}
%حدثنا \emphasize{هشيم}، أخبرنا \emphasize{إسماعيل بن أبي خالد}،
% عن أبي إسحاق، عن سعيد بن جبير، قال كنا
%    مع ابن عمر رضي الله عنه حيث أفاض من
%    عرفات إلى جمع فصلى بنا المغرب ومضى
%\end{arabtext}
%\setcode{standard}

@@

\subsection{Controller}
\label{sec:controller}
% FSM for the controller

We illustrate the hadith case-based controller 
in Figure~\ref{f:hadith}. 
The transitions in the hadith controller are excited
by inputs from the Sarf morphological analyzer. 
A NAME label means that Sarf encountered a proper name.
An NRC label means that Sarf met a narrator connector such as
\RL{`an} "on behalf of", \RL{.hada_t} "narrated", \RL{qaal} "said", 
\RL{'a_hbar} "told" or one of their derivations. 
The IBN label corresponds to the word \RL{ibn} "the son of" and is a name connector.
The NISBA label corresponds to an adjective that points to a person such 
as \RL{alma.sriy} "the Egyptian".

@@

The controller has four states that correspond to 
an abstract position in text relative to the next sanad. 
State TEXT\_S is the initial state and denotes that
the controller is outside the context of a sanad.
The controller moves to the state NAME\_S whenever
NAME is reported by Sarf.
State NRC\_S means that the controller thinks it is in the context
of a narrator name after Sarf reports an NRC.
State NMC\_S
indicates that the controller expects a name to appear within 
a tolerance threshold expressed by 
$\tau_{\mbox{NMC}}$ and $\lambda_{\mbox{NMC}}$.

\begin{figure}[tb!]
\center{
\resizebox{.9\columnwidth}{!}
{ \input{psfigs/hadith.pstex_t}}
\caption{The controller of the hadith case study.}
\label{f:hadith}
}
\end{figure}

@@

The controller reports a valid chain of narrators when a sequence of names
connected by narrator connectors appears. 
It marks the beginning of the hadith with the beginning of the current sequence,
and marks the end of the hadith with the beginning of the next sequence. 
It also marks the chain of narrators as the sequence itself.

The definition of input labels such as NAME and IBN depends on the 
morphological analyzer. 
However, our case-based controller approach was able to perform well
under both Sarf and a refined version of Sarf.

@@

\begin{table*}[bt]
\centering
\caption{Results of the hadith case study with Sarf.}
%\begin{tabular}{|p{1.5cm}||c|c||c|c||c|c|} \hline
\begin{tabular}{lp{.2cm}ccp{.2cm}ccp{.2cm}cc} %\cline{2-10}
 & & \multicolumn{2}{c}{Al Kafi} & & \multicolumn{2}{c}{Al Istibsar} & &\multicolumn{2}{c}{Ibn Hanbal} \\ \cline{3-10}
 & & Simple & Refined & & Simple & Refined & & Simple  & Refined \\\bottomrule  %\hline \hline
Word count & &\multicolumn{2}{c}{98,943} & & \multicolumn{2}{c}{103,835} & & \multicolumn{2}{c}{20,354} \\ 
 Names      & & 20,473 & 12,060  & &20,646 &  14,613& & 4,762 & 3,013\\
Names/Narrator& &2.48 & 1.97 & & 2.17 &  1.84& & 1.49 & 1.25 \\
Narrators & &3,080 & 2,623 & & 6,164 &  5,767& & 2,082 & 1,755 \\ 
Narrators/Chain & & 5.28 & 4.84 & & 4.98&  4.76 & & 4.8 &4.05 \\
Chains & & 583 & 542 &  & 1,238& 1,211& & 433 & 433 \\ 
Ignored names & & 11,801 & 6,400 &  & 5,845 & 3,348 & & 1,386 & 642 \\ \hline
Segmentation accuracy & & 85\% & 96\%& & 96\%& 96\%& & 92\%& 92\%\\ 
Chain accuracy & & 99\% & 99\%&  & 98\%& 99\%& & 99\% & 97\% \\ 
%Narrator accuracy & & & & & &  & & & \\ 
Narrator name accuracy & & 93\% & 91\%& &  92\%& 90\% & & 90\% & 90\% \\ \hline
Name false positives & & 28\% & 7\%&  & 9\%& 4\% & & 34\% & 4\% \\ \hline
Sarf running time (secs.)& & 2.97 & 1.32 & & 2.93 & 1.31 & & .25 & .096\\ \hline \hline
 & & Buckwalter& ElixirFM & & Buckwalter & ElixirFM & & Buckwalter & ElixirFM \\\bottomrule
Names      & & 18,354 & 19,201 & & 17,934 &  18,202 & & 5,021 & 5,117 \\
Names/Narrator& & 2.6 & 2.1 & & 2.47 &  2.07 & & 1.83 & 1.62\\
Narrators & & 3,210 & 2,981 & & 6,425 &  6,208 & & 2,311 & 1,965 \\ 
Narrators/Chain & & 5.57 & 5.32 & & 5.46 &  5.32 & & 5.12 & 5.01 \\
Chains & & 627 & 601 &  & 1,318 & 1,250 & & 487 & 452 \\ 
Ignored names & & 9,642 & 9,915 &  & 6,118 & 6,874 & & 1,812 & 1,904 \\ \hline
Segmentation accuracy & & 76\%& 84\%& & 85\%& 89 \%& & 84\%& 85\%\\ 
Chain accuracy & & 78\% & 87\%&  & 87\%& 90\%& & 85\% & 86\% \\ 
%Narrator accuracy & & & & & &  & & & \\ 
Narrator name accuracy & & 76\% & 86\%& & 84\%& 87\% & & 84\% & 84\% \\ \hline
Name false positives & & 29\% & 22\%&  & 14\%& 13\% & & 36\% & 32\% \\ \hline
Running time (secs.)& & 6.65 & 12$\times$60& &4.55 & 14$\times$60 & & .66 & 6$\times$60 
\end{tabular}
\normalsize
\label{t:hadithresallresults}
\end{table*}

In section we present results that compare Sarf to existing 
morphological analyzers such as Buckwalter and ElixirFM. 
We also evaluate our hypothesis of the utility of a case-based 
morphological analyzer,
by running our case study in two modes, simple and refined.
We ran our experiments using a dual core 2.66 Ghz 64-bit processor 
with 4GB of memory using a Linux operating system.

In the simple mode, Sarf is controlled by the hadith controller.
In the refined mode, we apply several refinements to Sarf.
The first refinement ignore female proper names except at the end of
a chain since they do not occur often in narrator names in hadith while
they can be common in early narrators such as the wives of the prophet.
We also add a refinement that detects compound proper names 
such as \RL{`bd alr.hmn} 
as they are common in narrator names.
Finally, we consider a possessive form as a reference to a person and treat
it as a narrator.

@@

\subsection{Comparison with Buckwalter and ElixirFM}

We implemented our case study with Buckwalter in two phases. 
In phase one, we process the entire text with Buckwalter and
obtain annotations to locations in text. 
Then in the second phase we feed these annotations to 
our controller as if they were coming from Sarf. 
We measure the time it took to produce the annotations
and the time it took the controller to process the 
annotations whithout the time spent streaming the annotations.
We used the same setup for ElixirFM.

Sarf outperforms both Buckwalter and ElixirFM in runing time. 
It also produces higher accuracy measures. 
We think this is mainly due to the extended
lexicon as well as to the fact that Sarf reduces false positive
names by ignoring prefixes and suffixes that can not form
names even if the stem was a name. 
Doing the same with Buckwalter and ElixirFM requires  
expanding the annotations resulting from one affix to reflect
its multiple composing affixes.
This is easily done with the way we defined affixes recursively.

Buckwalter performed much better than ElixirFM. This is up to 
our knowledge the first comparison of these two tools and 
we think the big difference is due to the more exact 
and grammar based functional morphological analysis ElixirFM 
uses.

\section{Conclusion and Future Work}
\label{sec:future}

@@

\section{Acknoledgements}
\label{sec:acc}
We thank the Lebanese National Council for Scientific Research (LNCSR) for funding this research.
